Ludwig User Tutorial

### 2018-09-25 docs/tutorial/tutorial.tex
Updated access information

The system requirements are an up-to-date version of a C compiler as well as working installations 
of a text editor like \texttt{vi} or \texttt{emacs}, Apache's Subversion (SVN) version control system, the visualisation tool
ParaView (\hyperref[ParaView]{https://www.paraview.org}), the MPI-library 
for compiling the parallel version of the code and \texttt{gnuplot} for simple visualisations.

@@

The \texttt{Ludwig} project is currently hosted at our central repository 
at CCPForge:\\
(\hyperref[CCPForge]{https://ccpforge.cse.rl.ac.uk}).\\
For full access to the repository please open a CCPForge account and request
to join the project \texttt{Ludwig}. The following command grants anonymous access:

\begin{lstlisting}[style=terminalverbatim]
$ svn checkout https://ccpforge.cse.rl.ac.uk/svn/ludwig
\end{lstlisting}

>>>>

The system requirements are an up-to-date version of a C compiler as well as working installations 
of a text editor like \texttt{vi} or \texttt{emacs}, the visualisation tool
ParaView (\hyperref[ParaView]{https://www.paraview.org}), the MPI-library 
for compiling the parallel version of the code and \texttt{gnuplot} for simple visualisations.

@@

The \texttt{Ludwig} project is currently hosted at our central repository at GitHub:\\
(\hyperref[GitHubLudwig]{https://github.com/ludwig-cf/ludwig}).\\

\smallskip
You can either download or clone the repository. 
The following command clones the repository into \texttt{ludwig} and requires a working 
git installation on your local system:

\begin{lstlisting}[style=terminalverbatim]
$ git clone https://github.com/ludwig-cf/ludwig
\end{lstlisting}
